\textls[-0]{\thetitle}

### 2023-02-28 body.tex
move appendices to tr
ref to appendices
small edits
ack

@@

@@

\section{More Typing Rules for \TT}
\input{all-typing-rule.tex}

@@

\section{Using \TT's Linkage Transformers to Model a Derived Family}
\input{stlc-linkTran-typing.tex}

@@

\section{The Complete Formalization and Proofs Written in Agda Syntax}
\label{sec:agda-files}
\input{agda-files.tex}

\if 0
\section{Metatheory, in detail}
\label{sec:metatheory}
\input{metatheory.tex}

\section{Example in Metatheory}
\label{sec:coqexample}
\input{coq-example.tex}

>>>>

\ifacknowledgments
\section*{Acknowledgments}
We thank the reviewers for their many useful comments.  We thank
Anastasiya Kravchuk-Kirilyuk, Yao Li, and Andrew Myers % others?
for valuable discussions.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.
\fi

@@

\ifreport

@@

\section{More Typing Rules for \TT}
\label{sec:more-rules}
\input{all-typing-rule.tex}

@@

\section{Using \TT's Linkage Transformers to Model a Derived Family}
\label{sec:lt-in-action}
\input{stlc-linkTran-typing.tex}

@@

\section{Definitive Version of the Formalization and Proofs}
\label{sec:agda-files}
\input{agda-files.tex}

%\section{Metatheory, in detail}
%\label{sec:metatheory}
%\input{metatheory.tex}
%
%\section{Example in Metatheory}
%\label{sec:coqexample}
%\input{coq-example.tex}
